KidsAIR: manuscript tables/figures

### 2020-12-24 main_analysis_final.Rmd
filter compliance data updates

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 16 Dec 2020"
output: pdf_document
---

@@

analysis_data <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         lrti_events_di_total = as.factor(lrti_events_di_total),
         person_time_at_risk_iqr = person_time_at_risk/20,
         child_age = factor(child_age, levels = c("< 1", "1+"))) 
  #filter(gender == "Female")
  #filter(home_sqft_2level == "1500+")

@@

analysis_data_winter1 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         lrti_events_di_winter = as.factor(lrti_events_di_winter),
         child_age = factor(child_age, levels = c("< 1", "1+"))) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  filter(winter_id == 1)

@@

itt_filter_comp_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + kw_perc_exp_cat2 + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)
write_rds(itt_filter_comp_results, paste0(file_path, "Output/itt_filter_comp_results.rds"))

@@

itt_pm_filter_comp_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                  child_age + (1 | cohort:area) + 
                                  kw_perc_exp_cat2, data = analysis_data_winter1)
write_rds(itt_pm_filter_comp_results, paste0(file_path, "Output/itt_pm_filter_comp_results.rds"))

>>>>

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 23 Dec 2020"
output: pdf_document
---

@@

analysis_data <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         lrti_events_di_total = as.factor(lrti_events_di_total),
         person_time_at_risk_iqr = person_time_at_risk/20,
         child_age = factor(child_age, levels = c("< 1", "1+"))) 
  #filter(area == "WMT")
  #filter(gender == "Female")
  #filter(home_sqft_2level == "1500+")

@@

analysis_data_winter1 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         lrti_events_di_winter = as.factor(lrti_events_di_winter),
         child_age = factor(child_age, levels = c("< 1", "1+"))) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  #filter(area == "WMT") %>% 
  filter(winter_id == 1)

@@

itt_filter_comp_results <- glmer(lrti_events_di_total ~ filter_compliance + 
                     child_age + person_time_at_risk + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)
summary(itt_filter_comp_results)
write_rds(itt_filter_comp_results, paste0(file_path, "Output/itt_filter_comp_results.rds"))

@@

itt_pm_filter_comp_results <- glmer(log(pm_mean_sampling_period) ~ filter_compliance + 
                                  child_age + (1 | cohort:area), 
                                  data = analysis_data_winter1)
write_rds(itt_pm_filter_comp_results, paste0(file_path, "Output/itt_pm_filter_comp_results.rds"))

### 2020-12-24 main_analysis_initial.Rmd
filter compliance data updates

kids_kw_report_1obs <- read_rds(paste0(file_path, "Output/kids_kw_report_clean.rds")) %>% 
  group_by(home) %>% 
  mutate(mean_kw_per_exp = mean(kw_perc_expected, na.rm = TRUE)) %>% 
  ungroup() %>% 
  distinct(area, home, .keep_all = TRUE) %>% 
  mutate(kw_perc_exp_cat = cut(kw_perc_expected, 
                               breaks = c(0, 30, 56, 106, 1000),
                               labels = c("Q1", "Q2", "Q3", "Q4"))) %>% 
  dplyr::select(-home_winter_id, -treatment_assigned, -treatment_actual, -home_id)

kids_kw_report_2obs <- read_rds(paste0(file_path, "Output/kids_kw_report_clean.rds")) %>% 
  group_by(area, home_winter_id) %>% 
  mutate(mean_kw_per_exp = mean(kw_perc_expected, na.rm = TRUE)) %>% 
  ungroup() %>% 
  distinct(area, home_winter_id, .keep_all = TRUE) %>% 
  mutate(kw_perc_exp_cat = cut(kw_perc_expected, 
                               breaks = c(0, 29, 53, 96, 1000),
                               labels = c("Q1", "Q2", "Q3", "Q4"))) %>% 
  dplyr::select(-home_winter_id, -treatment_assigned, -treatment_actual, -home_id)

@@

# Merge dataset with blinded treatments and final LRTI data, select analysis variables
kids_analysis_data_1obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_1obs_total, by = c("area", "home", "child_id_num")) %>% 
  left_join(kids_kw_report_1obs, by = c("area", "home")) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_num, child_age, lrti_events_total, 
         person_time_at_risk_total, lrti_incidence_total, newtx, treatment_assigned,
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti, gender,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level, home_sqft_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, 
         pm_sample_interval, pm_at_home_sampling_period,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5,
         home_act_smoking_sum, home_act_windows_sum, home_act_sweep_sum, home_act_door_sum,
         filter_type, mean_kw_per_exp, kw_perc_exp_cat) %>% 
  rename(treatment = newtx,
         person_time_at_risk = person_time_at_risk_total) %>% 
  mutate(log_person_time_at_risk = log(person_time_at_risk)) %>% 
  mutate(lrti_events_di_total = if_else(lrti_events_total == 0, 0, 1),
         treatment_filter_type = as.character(treatment_assigned),
         filter_type = as.character(filter_type),
         treatment_filter_type = if_else(treatment_filter_type == "Filter", 
                                         filter_type, treatment_filter_type),
         treatment_filter_type = factor(treatment_filter_type,
                                        levels = c("Placebo", "Education", 
                                                   "Honeywell", "Large Filtrete", 
                                                   "Small Filtrete", "Winix")),
         kw_perc_exp_cat2 = as.character(kw_perc_exp_cat),
         kw_perc_exp_cat2 = if_else(treatment_assigned == "Filter", kw_perc_exp_cat2, treatment_assigned),
         kw_perc_exp_cat2 = factor(kw_perc_exp_cat2,
                                  levels = c("Placebo", "Education", "Q1", "Q2", "Q3", "Q4"))) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))

@@

kids_analysis_data_2obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_1obs_per_winter, by = c("area", "home", "child_id_num", "winter_id")) %>%  
  left_join(kids_kw_report_1obs, by = c("area", "home", "winter_id")) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_num, home_winter_id, winter_id, child_age, 
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti, gender,
         lrti_events_winter, person_time_at_risk_winter, lrti_incidence_winter, newtx, treatment_assigned,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level, home_sqft_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, 
         pm_sample_interval, pm_at_home_sampling_period,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5,
         home_act_smoking_sum, home_act_windows_sum, home_act_sweep_sum, home_act_door_sum,
         filter_type, mean_kw_per_exp, kw_perc_exp_cat) %>% 
  rename(treatment = newtx) %>% 
  mutate(log_person_time_at_risk_winter = log(person_time_at_risk_winter)) %>% 
  mutate(lrti_events_di_winter = if_else(lrti_events_winter == 0, 0, 1),
         treatment_filter_type = as.character(treatment_assigned),
         filter_type = as.character(filter_type),
         treatment_filter_type = if_else(treatment_filter_type == "Filter", 
                                         filter_type, treatment_filter_type),
         treatment_filter_type = factor(treatment_filter_type,
                                        levels = c("Placebo", "Education", 
                                                   "Honeywell", "Large Filtrete", 
                                                   "Small Filtrete", "Winix")),
         kw_perc_exp_cat2 = as.character(kw_perc_exp_cat),
         kw_perc_exp_cat2 = if_else(treatment_assigned == "Filter", kw_perc_exp_cat2, treatment_assigned),
         kw_perc_exp_cat2 = factor(kw_perc_exp_cat2,
                                  levels = c("Placebo", "Education", "Q1", "Q2", "Q3", "Q4"))) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))

>>>>

kids_filter_compliance_total <- read_rds(paste0(file_path, "Output/kids_filter_compliance_total.rds")) %>% 
  dplyr::select(-home_winter_id, -winter_id, -treatment_assigned)

kids_filter_compliance_winter1 <- read_rds(paste0(file_path, "Output/kids_filter_compliance_winter1.rds")) %>% 
  dplyr::select(-home, -treatment_assigned, -winter_id)

@@

# Merge dataset with blinded treatments and final LRTI data, select analysis variables
kids_analysis_data_1obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_1obs_total, by = c("area", "home", "child_id_num")) %>% 
  left_join(kids_filter_compliance_total, by = c("area", "home")) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_num, child_age, lrti_events_total, 
         person_time_at_risk_total, lrti_incidence_total, newtx, treatment_assigned,
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti, gender,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level, home_sqft_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, 
         pm_sample_interval, pm_at_home_sampling_period,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5,
         home_act_smoking_sum, home_act_windows_sum, home_act_sweep_sum, home_act_door_sum,
         filter_type, filter_compliance) %>% 
  rename(treatment = newtx,
         person_time_at_risk = person_time_at_risk_total) %>% 
  mutate(log_person_time_at_risk = log(person_time_at_risk)) %>% 
  mutate(lrti_events_di_total = if_else(lrti_events_total == 0, 0, 1),
         treatment_filter_type = as.character(treatment_assigned),
         filter_type = as.character(filter_type),
         treatment_filter_type = if_else(treatment_filter_type == "Filter", 
                                         filter_type, treatment_filter_type),
         treatment_filter_type = factor(treatment_filter_type,
                                        levels = c("Placebo", "Education", 
                                                   "Honeywell", "Large Filtrete", 
                                                   "Small Filtrete", "Winix")),
         filter_compliance2 = as.character(filter_compliance),
         filter_compliance2 = if_else(treatment_assigned == "Education", treatment_assigned, filter_compliance2),
         filter_compliance = factor(filter_compliance2,
                                  levels = c("Placebo", "Education", 
                                             "0-25 compliance", "25-50 compliance",
                                             "50-75 compliance", "75-100 compliance"))) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))

@@

kids_analysis_data_2obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_1obs_per_winter, by = c("area", "home", "child_id_num", "winter_id")) %>%  
  left_join(kids_filter_compliance_winter1, by = c("area", "home_winter_id")) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_num, home_winter_id, winter_id, child_age, 
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti, gender,
         lrti_events_winter, person_time_at_risk_winter, lrti_incidence_winter, newtx, treatment_assigned,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level, home_sqft_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, 
         pm_sample_interval, pm_at_home_sampling_period,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5,
         home_act_smoking_sum, home_act_windows_sum, home_act_sweep_sum, home_act_door_sum,
         filter_type, filter_compliance) %>% 
  rename(treatment = newtx) %>% 
  mutate(log_person_time_at_risk_winter = log(person_time_at_risk_winter)) %>% 
  mutate(lrti_events_di_winter = if_else(lrti_events_winter == 0, 0, 1),
         treatment_filter_type = as.character(treatment_assigned),
         filter_type = as.character(filter_type),
         treatment_filter_type = if_else(treatment_filter_type == "Filter", 
                                         filter_type, treatment_filter_type),
         treatment_filter_type = factor(treatment_filter_type,
                                        levels = c("Placebo", "Education", 
                                                   "Honeywell", "Large Filtrete", 
                                                   "Small Filtrete", "Winix")),
         filter_compliance2 = as.character(filter_compliance),
         filter_compliance2 = if_else(treatment_assigned == "Education", treatment_assigned, filter_compliance2),
         filter_compliance = factor(filter_compliance2,
                                  levels = c("Placebo", "Education", 
                                             "0-25 compliance", "25-50 compliance",
                                             "50-75 compliance", "75-100 compliance"))) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))

### 2020-12-24 manuscript_tables_figures.Rmd
filter compliance data updates

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment_assigned == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>%
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>%
  filter(winter_id == 1) %>% 
  filter(treatment_assigned == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  group_by(area) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

>>>>

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment_assigned == "Filter") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  dplyr::select(area, home, new_var) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>%
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>%
  filter(winter_id == 1) %>% 
  filter(treatment_assigned == "Filter") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  dplyr::select(area, home, new_var) %>% 
  group_by(area) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}
